### 2017-09-29 TF-vldb2018/sec-intro.tex

Another issue is that team formation is accompanied with a highly dynamic environment. It typically needs many labor efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We show this with an example.

>>>>

Another issue lies in that team formation is accompanied with a highly dynamic environment. It typically needs many efforts to find the ideal teams, and is common for professionals to refine patterns  (requirements) multiple rounds~\cite{SajjadPG12,HabibiP15}. Further, real-life graphs are often big and constantly evolve over time~\cite{FanWW13-tods}. We show this with an example.
